---
title: "Multi-Output Tasks with mlr3"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Multi-Output Tasks with mlr3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mlr3)
library(mlr3multioutput)
```

# mlr3multioutput

Storing and working with multi-output Tasks in `mlr3`.

Multi-output Tasks are tasks with multiple targets of possibly different task_types that share the same features (and therefore observations).

## Scope

The packages scope is currently to ...



## General API

## Task

```{r}
t = tsk("linnerud")
t
```


## Learner
git st
```{r}
l = lrn("multiout.featurelessq()")
l
```

## Train & Predict

```{r}
l$train(t)
p = l$predict(t)
p
```

## Score

```{r}
p$score()
```

## Measure

Current limitations:
- One one predict_type: "response"
- One of `minimize`, weights etc.
- score() output has to be a scalar.

```{r}
m1 = msr(
  "multiout.custom",
  measures = list("regr" = msr("regr.mse")),
  weights =  c(Pulls = 1, Squats = 0.3, Jumps = 2)
)
m1
```

```{r}
p$score(m1)
```

## with mlr3pipelines

- `po("splitmultiout")`: Splits a `TaskMultiOutput` into one `Task` for each target.

```{r}
po("splitmultiout")$train(list(t))
```

- `po("multioutunite")`: Unites a `Multiplicity` of per-target `Predictions` into a `PredictionMultiOutput`.

```{r}
po("multioutunite") # See example below.
```

- `po("multilrn")`: Applies one or several `Learner`s for each Task in a `Multiplicity`.

```{r}
po("multilrn", lrns = list(lrn("regr.rpart"), lrn("classif.rpart")))
```

### Approach 1: Multiplicity (same learner for all targets)

```{r}
gr = po("splitmultiout") %>>%
 lrn("regr.rpart") %>>%
 po("multioutunite")
gr = GraphLearner$new(gr)

gr$train(t)
gr$predict(t)
```

### Approach 2: Multiplicity (per-task-type)

**API**:

```{r}
gr = po("splitmultiout") %>>%
 po("multilrn", lrns = list(regr = lrn("regr.rpart"), classif = lrn("classif.rpart")))

gl = GraphLearner$new(gr)
gl$train(t)
prds = gl$predict(t)
prds
```

Unclear:
- What does the `ParamSet` look like? Just unite and prefix with id?

### Approach 3: Multiplicity (per-target)

Current problems:
  - How to map learners to targets?
  - Names are lost through  `multiplicitlyimply`

**Internals**

```{r}
gr = po("splitmultiout") %>>%
  po("multiplicityexply", outnum = 3) %>>%
  gunion(list(
    lrn("regr.rpart", id = "rp1"),
    lrn("regr.rpart", id = "rp2"),
    lrn("regr.rpart", id = "rp3")
 )) %>>%
 po("multiplicityimply", innum = t$target_names) %>>%
 po("multioutunite")

gl = GraphLearner$new(gr)
gl$train(t)
prds = gl$predict(t)
prds
```

## with mlr3keras

**Not implemented**

```{r}
library(mlr3keras)
lrn("multiout.kerasff")
```


## Example Pipeline

```{r}
library(mlr3)
library(mlr3multioutput)
library(mlr3pipelines)
library(mlr3tuning)
library(paradox)

task = tsk("linnerud")

gr = PipeOpSplitMultiout$new() %>>% lrn("regr.rpart") %>>% PipeOpPredictionMultiOutUnite$new()

grl = GraphLearner$new(gr)

ps = ParamSet$new(
  list(
    ParamInt$new("regr.rpart.minsplit", lower = 1, upper = 100),
    ParamInt$new("regr.rpart.maxdepth", lower = 1, upper = 30)
  )
)

cv3 = rsmp("cv", folds = 3)

ms = MeasureMultiOutputWeightedAvg$new(measures = list(mse = msr("regr.mse")))

auto = AutoTuner$new(
  learner = grl,
  resampling = cv3,
  measure = ms,
  search_space = ps,
  terminator = trm("evals", n_evals = 20),
  tuner = tnr("random_search")
)

auto$train(task)
```


## TODOS

- Fix zzz.R, this seems sub-optimal, there should propably be unload and so on,
  look at other mlr3 packages.

- Document current limitations in Measure, predict_type etc.

- po("multilrn"): Tests and assert values are set correctly.

- Read up paper on multioutput evaluation.
